# ggplot

## Temas 
	- https://github.com/ricardo-bion/ggtech
	- https://jrnold.github.io/ggthemes/
	- Style used by the BBC News data team: https://github.com/bbc/bbplot/
	- https://ggplot2.tidyverse.org/reference/ggtheme.html

## Preenchimento, exemplo Histograma
REF: https://r-graphics.org/recipe-distribution-basic-hist

```{r}

# Set the width of each bin to 5 (each bin will span 5 x-axis units)
ggplot(faithful, aes(x = waiting)) +
  geom_histogram(binwidth = 5, fill = "white", colour = "black")

# Divide the x range into 15 bins
binsize <- diff(range(faithful$waiting))/15

ggplot(faithful, aes(x = waiting)) +
  geom_histogram(binwidth = binsize, fill = "white", colour = "black")

```

## Armazenar plots em DF
You don't HAVE to store your #dataViz as individual files.
You could dynamically generate plots for some combination of variables and store each #ggplot in a #tidyverse tibble.
E.g. if you are doing #bioinformatics and you want to plot-for-each-gene
Ref: https://twitter.com/jessenleon/status/1650564922630107136/


``` {r}

my_data <- palmerpenguins::penguins %>%
	drop_na %>%
	select( -year) %>%
	group_by(species, island) %>%
	nest %>%
	mutate( 
		my_plot = map(data, 
			~ggplot(
				data = .x,
				mapping = aes(x = bill_lenght_mm,
							  y = bill_depth_mm)) +
			geom_point() +
			labs( title = str_c(species, ",", island))))

my_data %>%
	pull(my_plot) %>%
	patchwork::wrap_plots()



### Alternativa de alocar os gráficos com uma lista
Ref: [How to create a list of plot objects and save them as files](https://cmdlinetips.com/2022/06/create-a-list-of-ggplot-objects-and-save-them-as-files/)


```{r }

plots <- penguins %>%
  split(.$species) %>%
  map(~ggplot(.x, aes(bill_length_mm, bill_depth_mm, color=sex)) + 
        geom_point()+
        theme_bw(16))

```

