---
title: "Tidy Data - Long and Wide format"
output: html_document
date: "2022-09-22"
---




3. Convert data from Wide to Long (and vice versa)

This step is also called data reshaping. 
Let’s create some data in wide format first.

```{r}
library(dplyr)
library(tidyr)

school_wide <- tibble(name = c("Stuart", "Bob", "Kevin"),
                      math = c(2, 3, 4),
                      sport = c(3, 1, 2),
                      art = c(3, 2, 1))
school_wide
```

### Convert Wide to Long Format

For the conversion the function pivot_longer() from tidyr package is used.

```{r}
school_tidy <- pivot_longer(data = school_wide,
                           cols = 2:4, 
                           names_to = "subject", 
                           values_to = "grade")
school_tidy
```

It consumes some parameters:

* data: the dataset to convert
* cols: the columns used for pivoting. You can specify numerical positions like here (2:4) or use functions like starts_with() to select all columns that start with a certain name.
* names_to: As the name suggests, this is the column holding the keys. So the column names are used in this step and will populate the values in this column.
* values_to: This defines the column name for the values from our wide format data.

### Convert Long to Wide Format

We make use of function pivot_wider() and store the result in an object called school_wide_reconstructed.

```{r}

school_wide_reconstructed <- pivot_wider(data=school_tidy, 
                                         id_cols = 'name', 
                                         names_from = 'subject', 
                                         values_from = 'grade')
school_wide_reconstructed
```

The function requires the following parameters:

* data: a data frame in long (tidy) format
* id_cols: the name of the columns which will be unchanged in the conversion
* names_from: the name of the column used to create column names
* values_from: the name of the column used to extract the values


